### 2018-04-08 reports/thesis/chapters/5_inference.tex
Modified value and figures output locations.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/nullhisto.eps}
	\caption{A histogram of simulated of 1\,000 null test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
	\label{fig:inference_nullhisto}
\end{figure}

A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_nullhisto}. The critical boundaries are also shown. In the uncorrected case, the critical region is $\|Z\|>2$. Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$. By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so. The Bonferroni correction performs well because it tested all the test statistics as negative correctly.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/nullpvalues.eps}
	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_nullpvalues}
\end{figure}

The ordered $p$-values are shown in Figure \ref{fig:inference_nullpvalues}. The $p$-values form a straight line as a result of being uniformly distributed. The critical line is $0.0455...\times\text{order}/1\,000$. This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results. In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure. As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{../figures/inference/althisto.eps}
	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
	\label{fig:inference_althisto}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/altpvalues.eps}
    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:altpvalues}
\end{figure}

In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated. The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_althisto}. The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario. However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../figures/inference/alt_z_critical.txt}$.

The ordered $p$-values are shown in Figure \ref{fig:altpvalues}. There are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.

This example shows a number of things. The BH procedure adapts to the data to control for the FDR. The uncorrected method did produce more positive results but at a cost of more false positives. It may seem unimpressive that the BH procedure only tested $\input{../figures/inference/alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.

@@

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate1}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
     \label{table:inference_error_rate1}
\end{table}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_image.eps}
        \caption{$z$ image with section highlighted}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo.eps}
        \caption{Histogram of section}
    \end{subfigure}
    }
    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
    \label{fig:inference_sub_z}
\end{figure}

A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}. One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}...$. However a quick look at the histogram will show that almost half of the pixels will be tested as positive. It is questionable whether such number of positive results is sensible, in particular in an area where defects are not expected.

@@

The method will be described here. Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$. First the histogram needs to be smoothed. \cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} will be used here because it has simpler mathematical properties. The kernel density estimate is
\begin{equation}
	\widehat{p}_Z(z)=
	\frac{1}{nh}
	\sum_{i=1}^n\phi\left(
		\dfrac{z_i-z}{h}
	\right)
	\label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
	\label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range. The parameters of the empirical null are estimated using the kernel density estimate. The resulting estimated density is shown in Figure \ref{fig:inference_sub_density_estimate}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_nocritical.eps}
        \caption{Histogram}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_parzen.eps}
        \caption{Kernel density estimate}
    \end{subfigure}
    }
    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate. The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
    \label{fig:inference_sub_density_estimate}
\end{figure}

Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is to be found. This is then used as the mean of the empirical null \citep{efron2004large}. The calculation of $\widehat{\mu}_0$ can be numerically found using the Newton-Raphson method. Using the mode, the standard deviation of the empirical null is estimated using \citep{efron2004large}
\begin{equation}
	\widehat{\sigma}_0 = \left[
		\left.
			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
		\right|_{z=\widehat{\mu}_0}
	\right]^{-1/2}
	\ .
\end{equation}
In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../figures/inference/sub_null_sigma.txt}...$. It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.

The empirical null is used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
\begin{equation}
	\zeta_i = \dfrac{
		z_i - \widehat{\mu}_0
	}
	{
		\widehat{\sigma}_0
	}
	\ .
	\label{eq:inference_zeta}
\end{equation}
The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ are then used in any multiple hypothesis testing procedures. Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../figures/inference/sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../figures/inference/sub_null_critical1.txt}...$ and $\input{../figures/inference/sub_null_critical2.txt}...\leqslant Z$.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_null.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_p_values.eps}
        \caption{Ordered $p$ values}
    \end{subfigure}
    }
    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
    \label{fig:inference_sub_z_critical_regions}
\end{figure}

These new critical regions are shown in Figure \ref{fig:inference_sub_z_critical_regions}. No positive results were found and the $p$-values are sensible as they look uniformly distributed. This demonstrated that the empirical null adjusts the parameters of the null distribution to fit the data in order to make sensible inference.

@@

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullhisto.eps}
	\caption{A histogram of simulated of 1\,000 null test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
	\label{fig:inference_multi_test_nullhisto}
\end{figure}

A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto}. The critical boundaries are also shown. In the uncorrected case, the critical region is $\|Z\|>2$. Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$. By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so. The Bonferroni correction performs well because it tested all the test statistics as negative correctly.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_multi_test_nullpvalues}
\end{figure}

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullpvalues}. The $p$-values form a straight line as a result of being uniformly distributed. The critical line is $0.0455...\times\text{order}/1\,000$. This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results. In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure. As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{../figures/inference/multi_test_althisto.eps}
	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
	\label{fig:inference_multi_test_althisto}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_altpvalues.eps}
    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_multi_test_altpvalues}
\end{figure}

In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated. The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto}. The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario. However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}$.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_altpvalues}. There are $p$-values below the critical line according to the BH procedure, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.

This example shows a number of things. The BH procedure adapts to the data to control for the FDR. The uncorrected method did produce more positive results but at a cost of more false positives. It may seem unimpressive that the BH procedure only tested $\input{../tables/multi_test_alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.

@@

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.txt}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate1}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.txt}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
     \label{table:inference_error_rate1}
\end{table}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_image.eps}
        \caption{$z$ image with section highlighted}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo.eps}
        \caption{Histogram of section}
    \end{subfigure}
    }
    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
    \label{fig:inference_empirical_null_sub_z}
\end{figure}

A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_empirical_null_sub_z}. One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../tables/empirical_null_sub_boundary.txt}...$. However a quick look at the histogram will show that almost half of the pixels will be tested as positive. It is questionable whether such number of positive results is sensible, in particular in an area where defects are not expected.

@@

The method will be described here. Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$. First the histogram needs to be smoothed. \cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} will be used here because it has simpler mathematical properties. The kernel density estimate is
\begin{equation}
	\widehat{p}_Z(z)=
	\frac{1}{nh}
	\sum_{i=1}^n\phi\left(
		\dfrac{z_i-z}{h}
	\right)
	\label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
	\label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range. The parameters of the empirical null are estimated using the kernel density estimate. The resulting estimated density is shown in Figure \ref{fig:inference_empirical_null_sub_density_estimate}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_nocritical.eps}
        \caption{Histogram}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_parzen.eps}
        \caption{Kernel density estimate}
    \end{subfigure}
    }
    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate. The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
    \label{fig:inference_empirical_null_sub_density_estimate}
\end{figure}

Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is to be found. This is then used as the mean of the empirical null \citep{efron2004large}. The calculation of $\widehat{\mu}_0$ can be numerically found using the Newton-Raphson method. Using the mode, the standard deviation of the empirical null is estimated using \citep{efron2004large}
\begin{equation}
	\widehat{\sigma}_0 = \left[
		\left.
			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
		\right|_{z=\widehat{\mu}_0}
	\right]^{-1/2}
	\ .
\end{equation}
In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$. It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.

The empirical null is used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
\begin{equation}
	\zeta_i = \dfrac{
		z_i - \widehat{\mu}_0
	}
	{
		\widehat{\sigma}_0
	}
	\ .
	\label{eq:inference_zeta}
\end{equation}
The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ are then used in any multiple hypothesis testing procedures. Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
        \caption{Ordered $p$ values}
    \end{subfigure}
    }
    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
    \label{fig:inference_empirical_null_sub_z_critical_regions}
\end{figure}

These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}. No positive results were found and the $p$-values are sensible as they look uniformly distributed. This demonstrated that the empirical null adjusts the parameters of the null distribution to fit the data in order to make sensible inference.

@@

The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more
